Improving \textsl{Gaia} parallax precision \\ with a data-driven model of stars

### 2017-06-06 paper/paper.tex
move citation

The lower main sequence is very narrow while the upper main sequence
is much wider. This may be an age variation on the main sequence mixed
with a Malmquist bias of seeing a much larger volume of upper main
sequence stars. There is a plausible binary sequence of stars with
about twice the brightness as the main sequence. The helium burning
red clump is prominent for the volume DR1 probed, and the red giant
branch is fairly straight and narrow. The main sequence turn off is
noticeable and also surprisingly narrow, possibly a reflection of the
star formation history of the local volume also mixed with a Malmquist
bias (\citealt{malmquist22}).

>>>>

The lower main sequence is very narrow while the upper main sequence
is much wider. This may be an age variation on the main sequence mixed
with a Malmquist bias of seeing a much larger volume of upper main
sequence stars \citep{malmquist22}. There is a plausible binary sequence of stars with
about twice the brightness as the main sequence. The helium burning
red clump is prominent for the volume DR1 probed, and the red giant
branch is fairly straight and narrow. The main sequence turn off is
noticeable and also surprisingly narrow, possibly a reflection of the
star formation history of the local volume also mixed with a Malmquist
bias.
